### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@6aa884bf0c127b4c10519179790bd9f30f30924b 🚀

Interactions between plants and pollinators form networks of
interactions, which together create the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The functioning and stability of ecosystems
emerge from these interactions, but anthropogenic change threatens to
unravel and ``rewire'' these interaction networks (CaraDonna \emph{et
al.} 2017), threatening the persistence of these systems.
Plant-pollinator networks face two possible forms of rewiring in
response to anthropogenic environmental change: spatial and temporal.
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer occur at the same time of year. This chapter uses
several years of data on bumblebee-flower phenology and interactions
across several field sites, each consisting of several plots across an
elevational gradient, combined with spatial records of species
occurrence via GBIF to forecast this uncoupling. This addresses the EBV
to forecast element of the flow from data to mitigation in
fig.~\ref{fig:thesis} (left).

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bauer2015QuiRev}{}%
Bauer, P., Thorpe, A. \& Brunet, G. (2015). The quiet revolution of
numerical weather prediction. \emph{Nature}, 525, 47--56.

>>>>

Interactions between plants and pollinators create networks of
interactions, which together form the ``architecture of biodiversity''
(Bascompte \& Jordano 2007). The functioning and stability of ecosystems
emerge from these interactions, but anthropogenic change threatens to
unravel and ``rewire'' these interaction networks (CaraDonna \emph{et
al.} 2017), threatening the persistence of these systems.
Plant-pollinator networks face two possible forms of rewiring in
response to anthropogenic environmental change: spatial and temporal.
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer occur at the same time of year. This chapter uses
several years of data on bumblebee-flower phenology and interactions
across several field sites, each consisting of several plots across an
elevational gradient, combined with spatial records of species
occurrence via GBIF to forecast this uncoupling. This addresses the EBV
to forecast element of the flow from data to mitigation in
fig.~\ref{fig:thesis} (left).

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
The Architecture of Biodiversity. \emph{Annual Review of Ecology,
Evolution, and Systematics}, 38, 567--593.

\leavevmode\hypertarget{ref-Bauer2015QuiRev}{}%
Bauer, P., Thorpe, A. \& Brunet, G. (2015). The quiet revolution of
numerical weather prediction. \emph{Nature}, 525, 47--56.
